Manuscript draft

### 2019-09-11 manuscript/Discussion_KAT.Rmd
Update Discussion_KAT.Rmd

One interesting observation was that climate explains more variation in the major fluxes (**LIST**) than in subsidiary fluxes (**LIST**) (Fig. 2; **some SI table?**). There are two non-exclusive potential explanations for this. First, it may be that methodological variation is larger relative to flux magnitude for some of the subsidiary fluxes. Belowground fluxes in particular are difficult to quantify, and measurement methods for the belowground fluxes considered here may be measured through fundamentally different approaches (*e.g.*, **ingrowth cores, XXX for $BNPP_{fine root}$; root exclusion, stable isotope tracking, or gas exchange of excised roots for $R_root$**), and sampling depth is variable and often insufficient to capture the full soil profile. $ANPP_{woody stem}$, which is also poorly explained by latitude or climate, is more straightforward to measure but is subject to variability introduced by differences such as biomass allometries applied, minimum plant size sampled, and exclusion or inclusion of branch fall (**REF**). However, methodological variation and uncertainty affects all of fluxes considered here--not necessarily any less than the aforementioned, and some of the larger fluxes that vary more strongly with respect to climate (ANPP, NPP) are estimated by summing uncertain component fluxes. Second, variation in the proportion of variability explained by climate could also indicate that factors other than climate have significant influence over subsidiary fluxes. This is consistent with the results we find for allocation between fluxes: although climate has a significant influence on subsidiary fluxes, it is not the only factor that is important, and many other local- and regional-scale factors  influence the way carbon is allocated between subsidiary fluxes. We would expect that this would reduce the strength of the effect of climate on subsidiary fluxes. [**work on this second part, add refs**]

@@

Despite the high standard of data quality in the ForC database, there are still significant limitations on our analyses. We standardised methodologies as far as possible, ensuring that there was consistency in the components included for each carbon flux. However, field techniques for estimating components of primary productivity are variable in their accuracy. This is particularly true for measures of BNPP, which are often estimated by extrapolating measures of ANPP. Even where BNPP is calculated through direct soil sampling, measures are often taken to insufficient depth, leading to underestimation of the flux. It is challenging to account for this type of variability in quality of field data, and our analyses largely assume good faith in data quality. While we have strong confidence in our analyses of well-understood fluxes, such as GPP, ANPP, and ANPP~woody~ ~stem~, we recommend caution in drawing firm conclusions from our analyses of BNPP, BNPP~fine~ ~root~, and, to some extent, NPP. We expect that, as field techniques improve the accuracy of estimates of these fluxes in the future, our understanding of the relationship of BNPP with climate variables will change. It is possible that the low R^2^ values for BNPP that we find are a result of lower accuracy in field measures of these fluxes, and that with improve standardisation of methods, we would find climate explains a higher proportion of variation.

>>>>

One interesting observation was that climate explains more variation in the major fluxes ($GPP$, $NPP$, $R_{auto}$ - latitude R^2≥48%) than in subsidiary fluxes (latitude R^2<27% for $BNPP_{fine.root}$, $R_{auto-root}$,$ANPP_{woody-stem}$) (Fig. 2; **some SI table?**). There are two non-exclusive potential explanations for this. First, it may be that methodological variation is larger relative to flux magnitude for some of the subsidiary fluxes. Belowground fluxes in particular are difficult to quantify, and measurement methods for the belowground fluxes considered here may be measured through fundamentally different approaches (*e.g.*, **minirhizotrons, ingrowth cores, or sequential coring for $BNPP_{root-fine}$; root exclusion, stable isotope tracking, or gas exchange of excised roots for $R_{auto-root}$**), and sampling depth is variable and often insufficient to capture the full soil profile. $ANPP_{woody-stem}$, which is also poorly explained by latitude or climate, is more straightforward to measure but is subject to variability introduced by differences such as biomass allometries applied, minimum plant size sampled, and exclusion or inclusion of branch fall (**REF**). However, methodological variation and uncertainty affects all of fluxes considered here--not necessarily any less than the aforementioned, and some of the larger fluxes that vary more strongly with respect to climate (ANPP, NPP) are estimated by summing uncertain component fluxes. Second, differences among variables in the proportion of variation explained by climate could indicate that factors other than climate have significant influence over subsidiary fluxes. This is consistent with the results we find for allocation between fluxes: although climate has a significant influence on subsidiary fluxes, it is not the only factor that is important, and many other local- and regional-scale factors  influence the way carbon is allocated between subsidiary fluxes. We would expect that this would reduce the strength of the effect of climate on subsidiary fluxes. [**work on this second part, add refs**]

@@
